Fitting metabolic models to dissolved oxygen data: the Estuarine BAyesian Single-station Estimation method

### 2023-05-04 manu-draft.qmd
scratch text to discussion

@@

-   Primary modifications (Production is linearly related to PAR (aPAR), not saturation point Respiration is constant (not temp dependent), Uses a gas exchange commonly used in oceanic systems (not littoral - streams/lakes as in Grace))
-   Describe how EBASE deals with gaps and flexibility of the model to accommodate diff optimization periods
-   b is sketchy, how to improve? Either fix or develop JAGS model further to include additional data, e.g. tidal height.
-   detiding - noise may produce higher and more variable metabolic rates
-   other main conclusions (from RGN comments on draft?)

>>>>

EBASE demonstrated on synthetic and obseved data that reasonable estimates .. EBASe was developed to address several critical needs in existing methods for estimating metabolism by 1) using a Bayesian framework, and 2) modifying several components of the underlying model with parameterizations more appropriate for estuarine settings. First, the Bayesian framework follows a an approach where the model is fit to the available data and allow for the incorporation of prior knowledge in teh model fitting process. ... The advantages of such an approach has led to widespread adoption of Bayesian approaches over frequentist approaches, especially in the coastal and marine community,  yet they have not been explored in do data for estuaries.  We have demonstrated that even using uninformed priors, EBASE can reproduce .  However, an exception is b which was unstable . This result may be explained simply by lack of gas exchange signal in teh DO time series that could be dominated by production and respiration.  Caffrey et al. suggest... EBASE could be applied in other settings where gas exchange may be expected to have a strong influence (windy). Or, more constrained priors could be used.

The second improvement of EBASE over alternative methods was the several modifications to

Our results also showed that tidal advection... led to positive bias, more variation, previously shown by .... solution is to detide or further develop model to accomodate tidal heigh contribution

@@

-   other main conclusions (from RGN comments on draft?)
